HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ddd
figure

>>>>

\begin{figure*}

  \begin{tikzpicture}
    [level 1/.style={sibling distance=7.5em},
      level 2/.style={sibling distance=5em},
      level 3/.style={sibling distance=5em},
      level 4/.style={sibling distance=3em}]
    %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
    %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
  \node (ROOT) [label={B}] [fill=blue, circle] {}
  child {node (H3) [label={A}] [fill=yellow,circle] {}
    child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
    child {node (H1) [label={O}] [fill=orange,circle] {}
      child {node [label={}] {became} edge from parent node[left]  {}}
      child {node [label={}] {a} edge from parent node[left]  {}}
      child {node [label={}] {passion} edge from parent node[left]  {}}
    }
    child {node (H2) [label={A}] [fill=yellow,circle] {}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node {} edge from parent[draw=none] {}}
      child {node [label={}] {for} edge from parent node[left]  {}}
      child {node [label={}] {his} edge from parent node[left]  {}}
      child {node [label={}] {oldest} edge from parent node[left]  {}}
      child {node [label={}] {daughter} edge from parent node[left]  {}}
    }
  }
  child {node {} edge from parent[draw=none] {}}
  child {node (H4) [label={A}] [fill=yellow,circle] {}
    child {node [label={}] {she} edge from parent node[left]  {}}
      child {node [label={}] {attended} edge from parent node[left]  {}}
      child {node [label={}] {daily} edge from parent node[left]  {}}
      child {node [label={}] {lesssons} edge from parent node[left]  {}}
  }
  child {node [label={}] {and} edge from parent node[left]  {}}
  child {node (H5) [label={A}] [fill=yellow,circle] {}  
    child {node [label={}] {greatly} edge from parent node[left] {}}
    child {node [label={}] {improved} edge from parent node[left] {}}
  };

  \com{
  child {node (H1) [label={\#8}] [fill=black,circle] {}
    child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    }
    child {node (H2) [label={\#9}] [fill=black,circle] {}
      child {node  {} edge from parent[draw=none]}
      child {node  {} edge from parent[draw=none]}
      child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
      child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
      child {node [label={\#10}] [fill=black,circle] {}
        child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
        child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
        edge from parent node[right] {$A$}}
      %child {node {to Paris} edge from parent node[right] {$A$}}
      edge from parent node[left] {$H$}
    };
    \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
    }
  \end{tikzpicture}
\caption{\label{fig:ucca_example2}
  Sample UCCA annotation. Edge labels mark UCCA categories. \#$<$index$>$ marks the node
indices.}
\end{figure*}
